%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Software Engineer}
  {BRAC IT Services Ltd.}
  {Dhaka, Bangladesh}
  {Dec. 2024 -- Present}
  {
    \begin{cvitems}
      \item {Developed backend modules for a multi-tenant CRM \& Ticketing System using Spring Boot, PostgreSQL, Redis, RabbitMQ, \\and MinIO, focusing on scalable service design and reliability.}
      \item {Implemented REST APIs for ticket lifecycle operations (create/update/search) with integrated SLA/KPI tracking, automated \\assignment rules, and full audit logging.}
      \item {Designed event-driven workflows using RabbitMQ (notifications, audit, SLA stage changes) with DLQ handling, retry policies,\\ and message durability guarantees.}
      \item {Built secure JWT-based authentication with role--permission authorization and refresh token flows for high-volume enterprise users.}
      \item {Optimized system performance via Redis caching (sorted sets, hash maps) and PostgreSQL indexing strategies (GIN/pg\_trgm), \\significantly reducing query latency.}
      \item {Integrated MinIO-based attachment service with presigned URL mechanisms and maintained schema evolution using Flyway \\migrations.}
    \end{cvitems}
  }


\cventry
  {Independent Researcher — NLP Security \& LLM Safety}
  {Personal Project}
  {Dhaka, Bangladesh}
  {Sept. 2024 -- Present}
  {
    \begin{cvitems}
      \item {Investigating prompt injection and RAG poisoning attacks on open LLMs.}
      \item {Built dataset, crafted instruction data and trained detectors using Hugging Face.}
      \item {Experimenting with attack mitigation and dataset generalization methods.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
